Automated Example Oriented REST API Documentation

### 2017-11-03 case_study/case_study.tex
footnotes added + removed the dashes
adds changes based on fixes from Nils

\chapter{A Case Study of Web API Evolution}
\label{chapter:case_study}

\section{Abstract}
When applications are integrated using web APIs, changes on a web API may break the dependent applications. This problem exists because old versions of the APIs may no longer be supported, a lack of adequate documentation to upgrade to a newer version, and insufficient communication of changes. In this paper we conducted a case study of evolving Web APIs to investigate what changes are made between versions and how the changes are documented and communicated to the API users. The findings are a list of recommendations for practitioners and researchers based on API change profiles, versioning, documentation and communication approaches that are observed in practice. This study will help inform developers of evolving Web APIs to make decision about versioning, documentation and communication methods.

@@

Web APIs connect independently maintained applications. As a result, when a Web API evolves, all the integrated applications using the Web API may not be able to evolve on the same schedule. For example, in the case of the aforementioned business search portal, if the Google Maps API changes, it may also require the portal to change. This introduces unique challenges to the evolution of Web APIs compared because the evolution is out of the control of the API users. For example, API users of a local API can use a copy of an older version, but for evolving Web APIs, API users are forced to upgrade if older versions are no longer supported. Documentation of evolving Web APIs is an important topic for case study because of the unique challenges it presents. Web APIs are defined by their HTTP interface, including both HTTP headers as well as request and response data formats. As a result, for an evolving Web API, its documentation needs to indicate changes in any of these fields, unlike the local APIs, where typically no HTTP specific information is involved.

@@

In our case studies, we included two open-source Web APIs, WordPress and OpenStreetMap, because it gave us access to  their source code to study how versioning is actually implemented. Wordpress REST API is developed as a plugin for Wordpress. As a result, a new version of the Web API is released with a new version of the plugin and it all API clients are affected when a new version is deployed. The source code for OpenStreetMap.org Web API shows the use of configuration files for API Versioning. We found its implementation only allows for a single API version.

@@

We also investigated how the API documentation is generated. We found that, Web API documents are manually generated and updated, unlike the documentation for local APIs which are are typically auto-generated. For WordPress and OpenStreetMap, this is apparent from their source code, as we found the use of manually edited wiki and Markdown files to generate the documentation\footnote{\url{http://en.wikipedia.org/wiki/Markdown}}.

>>>>

\chapter{\texorpdfstring{A Case Study of Web API Evolution \protect\footnote{S. Sohan, C. Anslow, and F. Maurer, ``A case study of Web API evolution,'' in Proc. of IEEE World Congress on Services (SERVICES). IEEE, 2015, pp. 245-252.}}{S. Sohan, C. Anslow, and F. Maurer, ``A case study of Web API evolution,'' in Proc. of IEEE World Congress on Services (SERVICES). IEEE, 2015, pp. 245–252.}}
\label{chapter:case_study}

\section{Abstract}
When applications are integrated using web APIs, changes on a web API may break the dependent applications. This problem exists because old versions of the APIs may no longer be supported, a lack of adequate documentation to upgrade to a newer version, and insufficient communication of changes. In this paper we conducted a case study of evolving Web APIs to investigate what changes are made between versions and how the changes are documented and communicated to the API users. The findings are a list of recommendations for practitioners and researchers based on API change profiles, versioning, documentation, and communication approaches that are observed in practice. This study will help inform developers of evolving Web APIs to make decision about versioning, documentation and communication methods.

@@

Web APIs connect independently maintained applications. As a result, when a Web API evolves, all the integrated applications using the Web API may not be able to evolve on the same schedule. For example, in the case of the aforementioned business search portal, if the Google Maps API changes, it may also require the portal to change. This introduces unique challenges to the evolution of Web APIs because the evolution is out of the control of the API users. For example, API users of a local API can use a copy of an older version, but for evolving Web APIs, API users are forced to upgrade if older versions are no longer supported. Documentation of evolving Web APIs is an important topic for case study because of the unique challenges it presents. Web APIs are defined by their HTTP interface, including both HTTP headers as well as request and response data formats. As a result, for an evolving Web API, its documentation needs to indicate changes in any of these fields, unlike the local APIs, where typically no HTTP specific information is involved.

@@

In our case studies, we included two open-source Web APIs, WordPress and OpenStreetMap, because it gave us access to  their source code to study how versioning is actually implemented. Wordpress REST API is developed as a plugin for Wordpress. As a result, a new version of the Web API is released with a new version of the plugin and all API clients are affected when a new version is deployed. The source code for OpenStreetMap.org Web API shows the use of configuration files for API Versioning. We found its implementation only allows for a single API version.

@@

We also investigated how the API documentation is generated. We found that, Web API documents are manually generated and updated, unlike the documentation for local APIs which are typically auto-generated. For WordPress and OpenStreetMap, this is apparent from their source code, as we found the use of manually edited wiki and Markdown files to generate the documentation\footnote{\url{http://en.wikipedia.org/wiki/Markdown}}.

### 2017-11-03 cisco_study/cisco_study.tex
adds changes based on fixes from Nils

Researchers identified the documentation of APIs as both the primary source of information as well as the key obstacle for API usability \cite{Robillard_what_makes}. To this regard, researchers have identified the qualities of ``good API documentation'' as follows: complete, correct, includes thorough explanations and code examples, provides consistent presentation and organization \cite{Robillard_what_makes,Myers_study}. In our previous work, we introduced a novel technique and SpyREST, an implementation, based on an HTTP proxy server to automatically intercept example REST API calls and synthesize the data to produce REST API documentation to meet the aforementioned qualities \cite{DBLP:conf/kbse/SohanAM15}.

@@

The REST API is documented using SpyREST via automated tests. To evaluate the outcome of the documentation process using SpyREST, we've incorporated stakeholder feedback as well as collected metrics from the various log files associated with the development and deployment of API docs and the actual API changes. 25 API stakeholders from Cisco were invited via email to provide free form feedback about the API documentation and its underlying process via emails to the first author of this paper.

@@

\subsubsection{API Evolution}
The API was first launched with version v0 in February 2015, and a fully compatible version v1 was released in May, 2016. The monthly release notes have mentioned at least one API related change for 12 times out of a total of 18 publicly announced releases of the software. Internally, the automated functional tests for the API documentation have changed 95 times by 6 contributors (as per the version control logs). The actual number of internal API evolution before they are released is unknown since they often happen several times a day, and don't always involve a change in the functional tests. The version numbers v0 and v1 were left unchanged to release backward compatible new features and bug fixes. At present, the API serves 80,000 API calls on an average per day (as per the API call logs) and is  used by over a hundred enterprise customers that are globally distributed. The customers use the SpyREST generated documentation as the sole information source for learning the API features. The actual number of API client developers is not known at this time since multiple API client developers can be involved in writing an API client application for the customers.

@@

This example code is written using RSpec\footnote{\url{http://rspec.info}}, a Ruby based test framework. Line 1 mentions the API version, line 2 mentions the API resource of interest, and line 3 shows a human readable description of the test. On lines 5-7, an example HTTP patch API request is made using the method $API.patch$. Then, an example assertion is added on line 8. the $API$ class has capabilities to make the $patch$ HTTP request over an HTTP Proxy server. While using the proxy server, the $API$ class also sends the test description ``Moves computer to a group with given $connector_guid$ and $group_guid$'' with a SpyREST specific header to automatically map test description as the description of the API usage example. As discussed earlier, the SpyREST analyzers can inspect the HTTP request and response information with the custom headers to produce usable REST API documentation from this automated test code.

@@

\subsection{Maintaining Custom Content}
Based on the feedback on SpyREST by Cisco developers, we've learned both the benefits and drawbacks of using a wiki-like editor for custom content with the API documentation. The wiki within SpyREST allows the API developers to add rich content comprising of proses, images, tables, code fragments, and web links, etc. to explain concepts that are required to understand the API. One developer feedback (D1) mentioned the following about the wiki: \textbf{``Good customization on the overview of each resource.''} Developer D3 mentioned the following: \textbf{``Being able to edit the documentation in place, similar to a wiki works really well, effectively allowing an organization to crowd-source the job.''} For example, at Cisco, we've added an overview explaining API access information, rate-limit, and common approaches to perform pagination within the API actions as custom content.

@@

The first author on this paper is a member of the team at Cisco where the case study is performed. While it provides us with a unique insights, it also introduces a confirmation bias. Our results may include a selection bias since the results are based on a single single set of REST APIs. While the aforementioned feedback shows that REST API documentation process is effective for us, we have a lack understanding of the impact of the documentation on the API client developers. This case study needs to be replicated against REST APIs that are implemented by other organizations using different technologies to reduce our limitations.

>>>>

Researchers identified the documentation of APIs as both the primary source of information as well as the key obstacle for API usability \cite{Robillard_what_makes}. In this regard, researchers have identified the qualities of ``good API documentation'' as follows: complete, correct, includes thorough explanations and code examples, provides consistent presentation and organization \cite{Robillard_what_makes,Myers_study}. In our previous work, we introduced a novel technique and SpyREST, an implementation, based on an HTTP proxy server to automatically intercept example REST API calls and synthesize the data to produce REST API documentation to meet the aforementioned qualities \cite{DBLP:conf/kbse/SohanAM15}.

@@

The REST API is documented using SpyREST via automated tests. To evaluate the outcome of the documentation process using SpyREST, we have incorporated stakeholder feedback as well as collected metrics from the various log files associated with the development and deployment of API docs and the actual API changes. 25 API stakeholders from Cisco were invited via email to provide free form feedback about the API documentation and its underlying process via emails to the first author of this paper.

@@

\subsubsection{API Evolution}
The API was first launched with version v0 in February 2015, and a fully compatible version v1 was released in May, 2016. The monthly release notes have mentioned at least one API related change for 12 times out of a total of 18 publicly announced releases of the software. Internally, the automated functional tests for the API documentation have changed 95 times by 6 contributors (as per the version control logs). The actual number of internal API evolution before they are released is unknown since they often happen several times a day, and don't always involve a change in the functional tests. The version numbers v0 and v1 were left unchanged to release backward compatible new features and bug fixes. At present, the API serves 80,000 API calls on average per day (as per the API call logs) and is  used by over a hundred enterprise customers that are globally distributed. The customers use the SpyREST generated documentation as the sole information source for learning the API features. The actual number of API client developers is not known at this time since multiple API client developers can be involved in writing an API client application for the customers.

@@

This example code is written using RSpec\footnote{\url{http://rspec.info}}, a Ruby based test framework. Line 1 mentions the API version, line 2 mentions the API resource of interest, and line 3 shows a human readable description of the test. On lines 5-7, an example HTTP patch API request is made using the method $API.patch$. Then, an example assertion is added on line 8. the $API$ class has capabilities to make the $patch$ HTTP request over an HTTP Proxy server. While using the proxy server, the $API$ class also sends the test description ``Moves computer to a group with given \texttt{connector\_guid} and \texttt{group\_guid}'' with a SpyREST specific header to automatically map test description as the description of the API usage example. As discussed earlier, the SpyREST analyzers can inspect the HTTP request and response information with the custom headers to produce usable REST API documentation from this automated test code.

@@

\subsection{Maintaining Custom Content}
Based on the feedback on SpyREST by Cisco developers, we have learned both the benefits and drawbacks of using a wiki-like editor for custom content with the API documentation. The wiki within SpyREST allows the API developers to add rich content comprising of proses, images, tables, code fragments, and web links, etc. to explain concepts that are required to understand the API. One developer feedback (D1) mentioned the following about the wiki: \textbf{``Good customization on the overview of each resource.''} Developer D3 mentioned the following: \textbf{``Being able to edit the documentation in place, similar to a wiki works really well, effectively allowing an organization to crowd-source the job.''} For example, at Cisco, we have added an overview explaining API access information, rate-limit, and common approaches to perform pagination within the API actions as custom content.

@@

The first author on this paper is a member of the team at Cisco where the case study is performed. While it provides us with a unique insights, it also introduces a confirmation bias. Our results may include a selection bias since the results are based on a single set of REST APIs. While the aforementioned feedback shows that REST API documentation process is effective for us, we have a lack understanding of the impact of the documentation on the API client developers. This case study needs to be replicated against REST APIs that are implemented by other organizations using different technologies to reduce our limitations.

### 2017-11-03 demo_paper/demo_paper.tex
adds changes based on fixes from Nils

In this paper we present SpyREST which provides the necessary tool support to address the unique needs for RESTful API documentation. To this regard, in the next section we have discussed the design goals followed by a HTTP proxy server based prototype implementation to demonstrate an automated RESTful API documentation tool. We then present two use cases to show how API developers can use SpyREST to automatically generate and maintain RESTful API documentation. In the discussion, we compare SpyREST against other tools. We provide an analysis of how the requirements for SpyREST are derived in the related work section.

@@

The technology choice behind for our implementation of SpyREST components is based on our past experience of using these tools but the concepts behind SpyREST is not dependent on the aforementioned technology choice. As a proof of concept, SpyREST only analyzes JSON based API request and response payloads.

>>>>

In this paper we present SpyREST which provides the necessary tool support to address the unique needs for RESTful API documentation. In this regard, in the next section we discuss the design goals followed by a HTTP proxy server based prototype implementation to demonstrate an automated RESTful API documentation tool. We then present two use cases to show how API developers can use SpyREST to automatically generate and maintain RESTful API documentation. In the discussion, we compare SpyREST against other tools. We provide an analysis of how the requirements for SpyREST are derived in the related work section.

@@

The technology choice behind our implementation of SpyREST components is based on our past experience of using these tools but the concepts behind SpyREST is not dependent on the aforementioned technology choice. As a proof of concept, SpyREST only analyzes JSON based API request and response payloads.

### 2017-11-03 introduction.tex
adds changes based on fixes from Nils

\section{Research Goals}
The overarching goal of my research is to improve the current state of the process of REST API documentation process by automating the repeating manual steps in the aforementioned workflow. More specifically, I aimed to solve the following research goals:

\begin{itemize}
  \item \textit{RG1: To identify a set of REST API documentation requirements.} Existing research on API usability has derived a number of API documentation requirements primarily focusing on local APIs. Due to the structural and implementation differences between local and REST APIs, I aimed to identity REST API specific documentation requirements in my research. This has several implications as follows: having access to a scientifically derived list of REST API documentation requirements allows REST API developers to make an informed decision related to planning and execution of their documentation efforts. The requirements provide a background research that can be used by practitioners to compare and contrast existing REST API documentation tools while selecting an appropriate tool for their API. REST API documentation tool developers can also use the requirements to build necessary features.
  \item \textit{RG2: To develop and evaluate a technique to overcome the commonly observed challenges related to REST API documentation.} I aimed to devise a reusable technique so that REST APIs can be documented following the identified REST API documentation requirements without following manual or bespoke methods. It has the following implications: REST API developers can utilize the technique to overcome the common challenges with the generation and maintenance of their API documentation, and REST API client developers can access an API documentation.
\end{itemize}

\section{Research Objectives}
Related to RG1 and RG2, I aimed to address the following research questions as my objectives:

\begin{itemize}
  \item \textit{RO1: How are evolving REST APIs documented?} This question is aimed to analyze the gap between current industry practice around the documentation of evolving REST APIs and the proposed solutions from existing literature. This objective helped me to identify the research opportunity to work on unresolved problems related to REST API documentation.
  \item \textit{RO2: What are the requirements for usable REST API documentation?} This objective provides a necessary background for improving the state of REST API documentation process.
  \item \textit{RO3: What technique can be used to document REST APIs to meet the requirements?} This is the central research objective. I researched to develop a new technique that can fill the gap between existing REST API documentation methods and the identified requirements.
  \item \textit{RO4: Is the proposed technique a practical one for REST API developers?} A qualitative evaluation of the proposed technique in a real-world setup is needed to understand the feasibility and the shortcomings of the proposed technique from the perspective of the REST API developers.
  \item \textit{RO5: How does a documentation using the proposed technique impact REST API client developers?} This question investigates the impact of the proposed technique from the perspective of the REST API client developer effort and success rate while performing API tasks.
\end{itemize}

>>>>

\section{Research Goals}
The overarching goal of my research is to improve the current state of the process of REST API documentation process by automating the repeating manual steps in the aforementioned workflow. More specifically, I aim to solve the following research goals:

\begin{itemize}
  \item \textit{RG1: To identify a set of REST API documentation requirements.} Existing research on API usability has derived a number of API documentation requirements primarily focusing on local APIs. Due to the structural and implementation differences between local and REST APIs, I aim to identity REST API specific documentation requirements in my research. This has several implications as follows: having access to a scientifically derived list of REST API documentation requirements allows REST API developers to make an informed decision related to planning and execution of their documentation efforts. The requirements provide a background research that can be used by practitioners to compare and contrast existing REST API documentation tools while selecting an appropriate tool for their API. REST API documentation tool developers can also use the requirements to build necessary features.
  \item \textit{RG2: To develop and evaluate a technique to overcome the commonly observed challenges related to REST API documentation.} I aim to devise a reusable technique so that REST APIs can be documented following the identified REST API documentation requirements without following manual or bespoke methods. It has the following implications: REST API developers can utilize the technique to overcome the common challenges with the generation and maintenance of their API documentation, and REST API client developers can access an API documentation.
\end{itemize}

\section{Research Objectives}
Related to RG1 and RG2, I aim to address the following research questions as my objectives:

\begin{itemize}
  \item \textit{RO1: How are evolving REST APIs documented?} This question is aimed to analyze the gap between current industry practice around the documentation of evolving REST APIs and the propose solutions from existing literature. This objective helped me to identify the research opportunity to work on unresolved problems related to REST API documentation.
  \item \textit{RO2: What are the requirements for usable REST API documentation?} This objective provides a necessary background for improving the state of REST API documentation process.
  \item \textit{RO3: What technique can be used to document REST APIs to meet the requirements?} This is the central research objective. I researched to develop a new technique that can fill the gap between existing REST API documentation methods and the identified requirements.
  \item \textit{RO4: Is the proposed technique a practical one for REST API developers?} A qualitative evaluation of the proposed technique in a real-world setup is needed to understand the feasibility and the shortcomings of the proposed technique from the perspective of the REST API developers.
  \item \textit{RO5: How does a documentation using the proposed technique impact REST API client developers?} This question investigates the impact of the proposed technique from the perspective of the REST API client developer effort and success rate while performing API tasks.
\end{itemize}

### 2017-11-03 root.tex
footnotes added + removed the dashes
adds changes based on fixes from Nils

\documentclass[12pt]{ucalgthes1}
\usepackage[pdftex]{graphicx}
\usepackage[pdftex]{color}
\usepackage[letterpaper,top=1in, bottom= 1in, left= 1in, right= 1in]{geometry}
\usepackage{hyperref}
\usepackage{mathptmx}
\usepackage{listings}
\usepackage{url}
\usepackage[tableposition=top]{caption}
\usepackage{subcaption}
\usepackage{tikz,pgfplots,pgfplotstable}
\usetikzlibrary{shapes,arrows}
\usepackage{mathtools}
\usepgfplotslibrary{dateplot}
\usepgfplotslibrary{statistics}
\usepackage{courier}
\usepackage[square,numbers,sectionbib]{natbib}
\usepackage[sectionbib]{chapterbib}
\usepackage[numbib]{tocbibind}
\newcommand{\newblock}{}
\usepackage{eurosym}
\usepackage{multirow}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\lstset{upquote=true}
\usepackage{float}
\floatstyle{boxed}
\usepackage{blindtext}
\let\labelindent\relax
\usepackage{upquote}
\usepackage{mdframed}
%\usepackage{balance}
\usepackage{enumitem}

\title{Automated Example Oriented REST API Documentation}
%
%            Insert the correct information between the {}
%
\author{S M Sohan}
\thesisyear{2017}
\thesis{thesis}    % the word dissertation can be inserted between {}
\newcommand{\thesistitle}{Automated Example Oriented REST API Documenation}
\monthname{September}
\dept{GRADUATE PROGRAM IN COMPUTER SCIENCE}
\degree{DOCTOR OF PHILOSOPHY}
%
%                    End of supplied information
%
\begin{document}
\makethesistitle
\pagenumbering{roman}     % resets page counter to one
\setcounter{page}{2}
\chapter*{UNIVERSITY OF CALGARY \\ FACULTY OF GRADUATE STUDIES}
\thispagestyle{empty}
The undersigned certify that they have read, and recommend
to the Faculty of Graduate Studies for acceptance, a \Thesis\ entitled
``\thesistitle'' submitted by \Author\
in partial fulfillment of the requirements for the degree of
\Degree.\\

@@

In this thesis, I present and evaluate of a novel technique to solve REST API documentation requirements. I present a set of REST API documentation requirements by studying the existing literature and the current industry practice. From this study, I observed that REST APIs evolve frequently, but used a manual or bespoke approach for generating and maintaining their documentation. I present, \textit{SpyREST}, a reusable technique with a prototype implementation to automate the REST API documentation process with executable API usage examples. The technique involves the interception of example REST API calls using an HTTP proxy server to auto-generate an accurate and updated REST API documentation. I present an industrial evaluation of the proposed technique based on a period of eighteen months of production use. From this study, I found that it was feasible to leverage API test code to automatically generate an always-updated REST API documentation for evolving REST APIs with usage examples. To evaluate the impact of usage examples on REST API client developers, I performed a controlled study with experienced REST API developers. From this case study, I found that REST API client developers faced patterns of obstacles using REST APIs that can be reduced by including API usage examples in the API documentation, as suggested in the proposed technique.

The findings of this research can be used as a guideline by practitioners to automatically generate REST API documentation with usage examples. Researchers can extend the novel concept of using interception to automatically document API usage examples for other forms of APIs.

>>>>

\documentclass[12pt]{ucalgthes1}
\usepackage[pdftex]{graphicx}
\usepackage[pdftex]{color}
\usepackage[letterpaper,top=1in, bottom= 1in, left= 1in, right= 1in]{geometry}
\usepackage{hyperref}
\usepackage{mathptmx}
\usepackage{listings}
\usepackage{url}
\usepackage[tableposition=top]{caption}
\usepackage{subcaption}
\usepackage{tikz,pgfplots,pgfplotstable}
\usetikzlibrary{shapes,arrows}
\usepackage{mathtools}
\usepgfplotslibrary{dateplot}
\usepgfplotslibrary{statistics}
\usepackage{courier}
\usepackage[square,numbers,sectionbib]{natbib}
\usepackage[sectionbib]{chapterbib}
\usepackage[numbib]{tocbibind}
\newcommand{\newblock}{}
\usepackage{eurosym}
\usepackage{multirow}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\lstset{upquote=true}
\usepackage{float}
\floatstyle{boxed}
\usepackage{blindtext}
\let\labelindent\relax
\usepackage{upquote}
\usepackage{mdframed}
%\usepackage{balance}
\usepackage{enumitem}
\title{Automated Example Oriented REST API Documentation}
%
%            Insert the correct information between the {}
%
\author{S M Sohan}
\thesisyear{2017}
\thesis{thesis}    % the word dissertation can be inserted between {}
\newcommand{\thesistitle}{Automated Example Oriented REST API Documenation}
\monthname{September}
\dept{GRADUATE PROGRAM IN COMPUTER SCIENCE}
\degree{DOCTOR OF PHILOSOPHY}
%
%                    End of supplied information
%
\begin{document}
\makethesistitle
\pagenumbering{roman}     % resets page counter to one
\setcounter{page}{2}
\chapter*{UNIVERSITY OF CALGARY \\ FACULTY OF GRADUATE STUDIES}
\thispagestyle{empty}
The undersigned certify that they have read, and recommend
to the Faculty of Graduate Studies for acceptance, a \Thesis\ entitled
``\thesistitle'' submitted by \Author\
in partial fulfillment of the requirements for the degree of
\Degree.\\

@@

In this thesis, I present and evaluate a novel technique to solve REST API documentation requirements. I present a set of REST API documentation requirements by studying the existing literature and the current industry practice. From this study, I observed that REST APIs evolve frequently, but used a manual or bespoke approach for generating and maintaining their documentation. I present, \textit{SpyREST}, a reusable technique with a prototype implementation to automate the REST API documentation process with executable API usage examples. The technique involves the interception of example REST API calls from API test code using an HTTP proxy server to auto-generate an accurate and updated REST API documentation. I present an industrial evaluation of the proposed technique based on a period of eighteen months of production use. From this study, I found that it was feasible to leverage API test code to automatically generate an always-updated REST API documentation for evolving REST APIs with usage examples. To evaluate the impact of usage examples on REST API client developers, I performed a controlled study with experienced REST API developers. From this case study, I found that REST API client developers faced patterns of obstacles using REST APIs that can be reduced by including API usage examples in the API documentation, as suggested in the proposed technique.

The findings of this research can be used as a guideline for practitioners to automatically generate REST API documentation with usage examples. Researchers can extend the novel concept of using interception to automatically document API usage examples for other forms of APIs.

### 2017-11-03 spy_rest/spy_rest.tex
adds changes based on fixes from Nils

  \textbf{R7 - Collaborative}: SpyREST needs to allow people to collaborate on the API documentation so that questions and answers about APIs can coexist with the API documentation to to overcome the knowledge fragmentation \cite{Chen_who_asked}.

@@

\section{SpyREST Case Study}
\label{sec:case_study}
In this section we discuss a case study of using SpyREST to auto generate documentation for 25 API actions randomly sampled from three RESTful API providers. These 25 API APIs are documented using 272 lines of code\footnote{\url{https://github.com/smsohan/spyrest_examples}}. These three API providers are: GitHub.com, KISSMetrics.com (Online analytics tool), and LiquidPlanner.com (Online project management tool).

>>>>

  \textbf{R7 - Collaborative}: SpyREST needs to allow people to collaborate on the API documentation so that questions and answers about APIs can coexist with the API documentation to overcome the knowledge fragmentation \cite{Chen_who_asked}.

@@

\section{SpyREST Case Study}
\label{sec:case_study}
In this section we discuss a case study of using SpyREST to auto generate documentation for 25 API actions randomly sampled from three RESTful API providers. These 25 APIs are documented using 272 lines of code\footnote{\url{https://github.com/smsohan/spyrest_examples}}. These three API providers are: GitHub.com, KISSMetrics.com (Online analytics tool), and LiquidPlanner.com (Online project management tool).
